---
title: "Impact of Age On Academic Achievement"
author: "Yujing Fang, Chang Lian, Zhengdao Song"
date: "July 1, 2016"
output: html_document
---

rm(list=ls(all=TRUE))
# Load libraries
```{r}
library(dplyr)
```

# Load raw data
```{r}
# Read all raw data
data <- read.csv("result/reshaped_data.csv", stringsAsFactors = F)
```

# Exploratory Analysis
```{r}
# numbers of variables and numbers of observations
dim(data)

# structure of variables
str(data)

# Descriptive statistics
summary(data)

# Histogram
hist(data$current_age)
plot(density(data$current_age)) #kernel density estimate

hist(data$phd_age)
plot(density(data$phd_age))


hist(data$num_articles)
plot(density(data$num_articles))

hist(data$num_peered_reviewed_articles)
plot(density(data$num_peered_reviewed_articles))

hist(data$percent_peered_reviewed_articles)

# Create scatterplots for numeric metircs
data_numeric <- select(data, current_age, phd_age, current_university_rank, current_university_tier,num_articles, num_peered_reviewed_articles, percent_peered_reviewed_articles )

pairs(data_numeric,panel=panel.smooth)
```

# Percentage of Peers Reviewed Articles ~ Ages
Compared "centers" and "spreads" of Percentage of PR Articles across Ph.D Ages
```{r}
boxplot(percent_peered_reviewed_articles ~ phd_age, data=data, main="Boxplots of Percentage of Peers Reviewed Articles Across Ph.D Ages", xlab="Ph.D Age", ylab="Percentage of PR Articles")
```

Compared "centers" and "spreads" of Percentage of PR Articles across Current Ages
```{r}
boxplot(percent_peered_reviewed_articles ~ current_age, data=data, main="Boxplots of Percentage of Peers Reviewed Articles Across Current Ages", xlab="Current Age", ylab="Percentage of PR Articles")
```

# Percentage of Peers Reviewed Articles ~ Universities
Compared "centers" and "spreads" of Percentage of PR Articles across University Ranks
```{r}
boxplot(percent_peered_reviewed_articles ~ current_university_rank, data=data, main="Boxplots of Percentage of Peers Reviewed Articles Across University Ranks", xlab="University Rank", ylab="Percentage of PR Articles")
```

Compared "centers" and "spreads" of Percentage of PR Articles across University Tiers
```{r}
boxplot(percent_peered_reviewed_articles ~ current_university_tier, data=data, main="Boxplots of Percentage of Peers Reviewed Articles Across University Tiers", xlab="University Tier", ylab="Percentage of PR Articles")
```

# Linear Regression for num_articles
num_articles ~ current_age, phd_age, current_university_ranks
```{r}
rg_articles <- lm(num_articles ~ current_age + phd_age + current_university_rank, data = data)
summary(rg_articles)
```

# Linear Regression for log(num_articles)
log(num_articles) ~ current_age, phd_age, current_university_ranks
```{r}
# Create a replica of 'data' data frame for adding log(num_article)
data_log_num_articles <- data
data_log_num_articles$log_num_articles <- log(data_log_num_articles$num_articles)

# Drop -Inf
data_log_num_articles <- subset(data_log_num_articles, log_num_articles!= "-Inf")

# Run regression
rg_articles_log <- lm(log_num_articles ~ current_age + phd_age + current_university_rank, data = data_log_num_articles)
summary(rg_articles_log)
```


# Linear Regression for num_peered_reviewed_articles
num_peered_reviewed_articles ~ current_age, phd_age, current_university_ranks
```{r}
rg_peers_articles <- lm(num_peered_reviewed_articles ~ current_age + phd_age + current_university_rank, data = data)
summary(rg_peers_articles)
```

# Linear Regression for log(num_peered_reviewed_articles)
log(num_peered_reviewed_articles) ~ current_age, phd_age, current_university_ranks
```{r}
# Create a replica of 'data' data frame for adding log(num_article)
data_log_peers_articles <- data
data_log_peers_articles$log_num_peered_reviewed_articles <- log(data_log_peers_articles$num_peered_reviewed_articles)

# Drop -Inf
data_log_peers_articles <- subset(data_log_peers_articles, log_num_peered_reviewed_articles!= "-Inf")

# Run regression
rg_peers_articles_log <- lm(log_num_peered_reviewed_articles ~ current_age + phd_age + current_university_rank, data = data_log_peers_articles)
summary(rg_peers_articles_log)
```

# Linear Regression for percent_peered_reviewed_articles
percent_peered_reviewed_articles ~ current_age, phd_age, current_university_ranks
```{r}
rg_percent_peers <- lm(percent_peered_reviewed_articles ~ current_age + phd_age + current_university_rank, data = data)
summary(rg_percent_peers)
```

# Linear Regression for log(percent_peered_reviewed_articles)
log(percent_peered_reviewed_articles) ~ current_age, phd_age, current_university_ranks
```{r}
# Create a replica of 'data' data frame for adding log(num_article)
data_log_percent_peers <- data
data_log_percent_peers$log_percent_peered_reviewed_articles <- log(data_log_percent_peers$percent_peered_reviewed_articles)

# Drop -Inf & NaN
data_log_percent_peers <- subset(data_log_percent_peers, log_percent_peered_reviewed_articles!= "-Inf")
data_log_percent_peers <- subset(data_log_percent_peers, log_percent_peered_reviewed_articles!= "NaN")

# Run regression
rg_percent_peers_log <- lm(log_percent_peered_reviewed_articles ~ current_age + phd_age + current_university_rank, data = data_log_percent_peers)
summary(rg_percent_peers_log)
```


